Northern Pikeminnow Predation on Juvenile Chinook Salmon and Potential Impacts to Local Populations

### 2021-11-24 analysis/paper/paper.Rmd
moved a chunk of code

adult_impact = fall_only_no_growth %>%
  filter(cum_cons_fish_g == max(cum_cons_fish_g)) %>%
  select(cum_cons_fish_g) %>%
  mutate(n_chnk_smolts = cum_cons_fish_g / 12) %>%
  bind_cols(all_est %>%
              select(event_name, 
                     model,
                     N,
                     Lci,
                     Uci)) %>%
  mutate(across(c(smolt_N = N, 
                  smolt_Lci = Lci, 
                  smolt_Uci = Uci),
                ~ . * n_chnk_smolts)) %>%
  bind_cols(sar) %>%
  mutate(adult_N = smolt_N * medsar,
         adult_Lci = smolt_Lci * qnorm(0.025, medsar, sdsar),
         adult_Uci = smolt_Uci * qnorm(0.975, medsar, sdsar))
```

>>>>

adult_impact = fall_only_no_growth %>%
  filter(cum_cons_fish_g == max(cum_cons_fish_g)) %>%
  select(cum_cons_fish_g) %>%
  mutate(n_chnk_smolts = cum_cons_fish_g / 12) %>%
  bind_cols(all_est %>%
              select(event_name, 
                     model,
                     N,
                     Lci,
                     Uci)) %>%
  mutate(across(c(smolt_N = N, 
                  smolt_Lci = Lci, 
                  smolt_Uci = Uci),
                ~ . * n_chnk_smolts)) %>%
  bind_cols(sar) %>%
  mutate(adult_N = smolt_N * medsar,
         adult_Lci = smolt_Lci * qnorm(0.025, medsar, sdsar),
         adult_Uci = smolt_Uci * qnorm(0.975, medsar, sdsar))
